Cancer Applications of Choropleth Maps, and the Potential of Cartograms and Alternative Map Displays

### 2019-12-17 review_article.Rmd
conclusions

<!-- summary of mapping -->
This paper provides an overview of mapping practices as used for cancer atlases and new approaches that could be adopted. The conventional approach is the choropleth map, and it is widely used. When there are small areas, as occurs in Australia where the population is concentrated on the coast, the information about cancer can be lost, and alternatives are needed. Making an inset can clarify congested regions but this breaks the viewers' attention because they need to shift focus from the map to the inset, and if there are many congested areas, many insets would be needed. The map alternatives, like cartograms and their variations, can be useful to allow the spatial distribution of cancer data to be digested.

@@

<!-- interaction -->
Interaction with maps is an important component of public atlases. A purpose is to provide access to more information than is possible to display in a single map, without overwhelming the viewer. Too many choices though can similarly overwhelm a viewer, and thus decisions do need to be made about content to provide, or hide, for accurate and comprehensive communication of information. Similarly, providing ways for users to interact with the display encourages engagement, and creative, efficient, elegant, interactive tools elicit curiosity about the data.

>>>>

<!-- summary of mapping -->
This paper provides an overview of mapping practices as commonly used for cancer atlases and recommends new approaches, such as cartograms and hexagon tile maps that should be adopted going forward. The conventional approach is the choropleth map, and it is widely used. When there are small areas, as occurs in Australia where the population is concentrated on the coast, the information about cancer can be lost, and alternatives are needed. Making an inset can clarify congested regions but this breaks the viewers' attention because they need to shift focus from the map to the inset, and if there are many congested areas, many insets would be needed. The map alternatives, like cartograms and their variations, can be useful to allow the spatial distribution of cancer data to be digested.

@@

<!-- interaction -->
Interaction with maps is an important component of public atlases, and is easy to add with today's technology. A purpose is to provide access to more information than is possible to display in a single map, without overwhelming the viewer. Too many choices though can similarly overwhelm a viewer, and thus decisions do need to be made about content to provide, or hide, for accurate and comprehensive communication of information. Similarly, providing ways for users to interact with the display encourages engagement, and creative, efficient, elegant, interactive tools elicit curiosity about the data.
